% cover letter LaTeX template
\documentclass[10pt]{letter}
\usepackage{newcent}
\signature{Emil Johansson}
\address{Bredgatan 24C \\ Lund \\ Sweden}
\begin{document}
\begin{letter}{ARM Sweden\\ Emdalavägen 6\\ Lund\\ Sweden}
\opening{Dear Sir or Madam:}

Firstly, thank you for considering my application to your intern
program. I was almost starstruck when I realized that the ARM that
was popping up on my LU career page was {\bf the} ARM. I originally
did not intend to apply to any jobs this summer, as my own projects
have been more enticing than the jobs I have found, but this was
certainly an exception. I am exited with the prospect of spending this
summer learning and creating software in the ARM Media Processing
Group. 

The description of the position seemed to fit both my strengths and
passions. Thinking through complex, abstract problems is more or less
all we do studying the inner workings of nature at the physics
department. But also the passion that I have developed under the last
couple of years, software development.

Although physics is stimulating, it can not consume me like the
feeling of being able to control the power of computations. I have
studied programming in my physics degree, but most of my knowledge I
have acquired myself. Initially by reading { \it c++ direkt} by Jan
Skansholm cover to cover and then doing projects on the side of my
studies. It is not only writing working code that entice me but the
art of creating software that is maintainable and re-usable in
different contexts. 

At the ARM Media Group I hope to contribute with my strong
mathematical background and passion for software, and build on key
skills for my future studies and career. I prefer a summer position so
that I can focus my entire attention to the work. But I do not
categorically reject other possibilities.


\closing{Yours Faithfully,}
%\ps{P.S. Here goes your ps.}
%\encl{CV and/or Resume}
\end{letter}
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
