%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Undisclosed} % Organization
{Backend Software Engineer} % Job title
{Malmö, Sweden} % Location
{Feb. 2018 - present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Working with Python, Scala, and TypeScript.}
\item {Taking a technical leadership role in the team driving code quality
       and increased developer productivity and quality of deliverables.}
\item {Learned a lot about producing and releasing high quality
       software at fast pace in an enviroment with many stakeholders and
       unknowns.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Advenica} % Organization
{IT security solutions for critical infrastructure} % Job title
{Malmö, Sweden} % Location
{Sep. 2018 - Dec. 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Levering GNU/Linux and C/C++ knowledge as a consultant, developing support for a new protocol to their network segmentation products for critical infrastructure.}
\item {Learned a lot about the challenges of adopting agile development practices and continuous
integration in a security focused IT environment.}
\end{cvitems}
}

%------------------------------------------------    
\cventry
{Lund University, Solid State Physics, Theoretical Physics, and Mathematical Physics} % Organization
{Applying Machine Learning to mathematical physics } % Job title
{Lund, Sweden} % Location
{Sep. 2017 - Aug. 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Explored novel ways to reformulate constrained optimization into
machine learning, the results was interesting enough to warrant the ``NanoLund Junior Scientist Ideas Award''}
\item {Used to Google Cloud to fast scale up and down as demand for
computational power (both CPU and GPU) changed during the project.}
\end{cvitems}
}

\cventry
{Private Project} % Organization
{Full Stack Web Application } % Job title
{Lund, Sweden} % Location
{Mar. 2017 } % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Created a proof-of-concept ``Wikipedia band name generator'' web site
levering public APIs, python code, cloud hosting, and flask to automatically
generate silly band names and cover art.}
\end{cvitems}
}

\cventry
{Private Project} % Organization
{IOS and Desktop QT Application } % Job title
{Lund, Sweden} % Location
{Sep. 2016 } % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {My interest in automation resulted in that creating a Sudoku solver app
seems more fun than solving Sudoku manually so that is what I did.}
\item {Learned about connecting and separating back end a front end logic
as well as the QT framework }
\end{cvitems}
}

\cventry
{Lund University, Mathematical Physics} % Organization
{Numerical Simulations of Nunneries } % Job title
{Lund, Sweden} % Location
{Sep. 2016 } % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {  I wrote a code based on a quantum transport simulation library named
Kwant, simulating the effects of different contact geometries on
conductivity in nanowires. }
\item {First interaction with one of my now favorite design patterns. Writing
performance critical function calls in c/c++ and exposing them as python
functions for the high level logic.}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}
